---
title: "Masters results"
author: "Michael Giordano"
date: "April 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
# setup
rm(list=ls())
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(MIIVsem)
library(knitr)
library(kableExtra)
library(jtools)
options(knitr.table.format = "html") 
baseDir <- "c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults"
knitr::opts_knit$set(root.dir = baseDir )

# setwd(baseDir)
```

```{r design, include=FALSE}
# ------------------------------------------------------------------------
# read in simulation design matrix
dm <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/simparams.rds")
dm <- dm$designMatrix
# -----------------------------------------------------------------------
```

```{r, echo = FALSE, include = FALSE}
# names(dm)
# between cell conditions
kable(unique(dm[,c("clusterSize", "clusterN", "clusterBal", "skewKurt")]), row.names = FALSE)
# within cell conditions
kable(unique(dm[,c("modelSpec", "estimators")]), row.names = FALSE)
```

```{r plotfn, echo = FALSE}
# function to make sargan plot
makeSargPlot <- function(df, facetVar, title) {
  par(pin = c(6, 12))
  # saving names of the variables we need for sargans
wl <-c("L1 by Y1",
       "L1 by Y2",
       "L1 by Y3",
       "L1 by Y5",
       "L2 by Y4",
       "L2 by Y5",
       "L2 by Y6",
       "L2 by Y2")
bl <- c("LB by Y1",
       "LB by Y2",
       "LB by Y3",
       "LB by Y4",
       "LB by Y5",
       "LB by Y6")
names <- paste0(c(wl, bl), " sarg p")

# subset just the sargan p-value parameters
sarg <- l_sub[l_sub$parameter %in% names, ]

# take sarg out of parameter names
sarg$parameter <- gsub(" sarg p", "", sarg$parameter, fixed = TRUE)

# removing a few irrelevant columns
sarg <- sarg[,c("Iteration",
                "clusterSize",
                "clusterN",
                "clusterBal",
                "wSkew",
                "wKurt",
                "bSkew",
                "bKurt",
                "modelSpec",
                "estimators",
                "skewKurt",
                "skewKurt2",
                "seed",
                "dfName",
                "datName",
                "sampleSize",
                "rdsName",
                "inpName",
                "parameter",
                "est",
                "cluster")]
# subsetting complete cases
sarg <- sarg[complete.cases(sarg),]
sarg[sarg$est<=.05, "sarg.d"] <- 1
sarg[!sarg$est<=.05, "sarg.d"] <- 0

# summary
r <- sarg %>%
  group_by(cluster, clusterBal, skewKurt, skewKurt2, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            mean = mean(sarg.d))
# creating a level variable
r[grep("LB", r$parameter), "level"] <- "between"
r[grep("L1", r$parameter), "level"] <- "within"
r[grep("L2", r$parameter), "level"] <- "within"
# plotting
# plot <- ggplot(r, aes(x= cluster, y = mean, 
#                 group = interaction(parameter, estimators), 
#                 color = interaction(estimators, level))) + 
#                 geom_line() +
#                 geom_point()+
#                 # geom_jitter(width = .4) +
#                 # facet_grid(modelSpec~cluster, scales="free_x", space="free_x", shrink=TRUE, drop=TRUE) +  
#                 # facet_grid(modelSpec~cluster, scales="free_x", space="free_x") +   
#                 # stat_summary(fun.y = mean, geom="point",colour="darkred", size=1, 
#                 #              position = position_dodge(width = .75)) +
#                 # geom_hline(yintercept = .05) + 
#                 # geom_hline(yintercept = -20) + 
#                 geom_hline(yintercept = .05, color = "red", linetype = "dashed") +
#                 # coord_cartesian(ylim=c(0, .4)) +
#                 # scale_y_continuous(breaks = seq(from = 0, to = 1, by = .2)) +
#                 theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1)) +
#                 ylab("Alpha/Proportion reject null") +
#                 xlab("Sample Size") +
#                 ggtitle(title)

plot <- ggplot(r, aes(x=parameter, y = mean, color = estimators)) + 
                # geom_point() +
                geom_jitter(width = .2, size = 2) +
                # facet_grid(.~cluster, scales="free_x", space="free_x", shrink=TRUE, drop=TRUE) +
                facet_grid(as.formula(paste(".~", facetVar)), scales="free_x", space="free_x", shrink=TRUE, drop=TRUE) +  
                geom_hline(yintercept = .05, color = "red", linetype = "dashed") +
                coord_cartesian(ylim=c(0, 1)) +
                scale_y_continuous(breaks = seq(from = 0, to = 1, by = .1)) +
                scale_color_manual(values = c("#00BA38", "#619CFF"),
                                  name="Estimator",
                                  labels=c("Goldstein-MIIV", "MUML-MIIV")) +
                theme_apa() +
                theme(axis.text.x=element_text(angle=45,hjust=1,vjust=1),
                      legend.position = c(0.02,.75), 
                      legend.background = element_rect(linetype = 1, size = 0.5, colour = 1), 
                      legend.key.width = unit(.3, "in"),
                      legend.text = element_text(size = rel(.9))) +
                ylab("Sargan's Alpha/Proportion reject null") +
                xlab("Factor Loadings") #+
                #ggtitle(title)
return(plot)
}



makeRelBiasPlot <- function(df, facetVar) {
  wl <-c("L1 by Y1",
       "L1 by Y2",
       "L1 by Y3",
       "L1 by Y5",
       "L2 by Y4",
       "L2 by Y5",
       "L2 by Y6",
       "L2 by Y2")
bl <- c("LB by Y1",
       "LB by Y2",
       "LB by Y3",
       "LB by Y4",
       "LB by Y5",
       "LB by Y6")
  
  p <-  ggplot(df[df$parameter %in% c(wl, bl), ], aes(x=parameter, y = p_relBias, fill = estimators)) +
          geom_boxplot() +
          facet_grid(as.formula(paste(".~", facetVar)), scales="free_x", space="free_x", shrink=TRUE, drop=TRUE) +  
          stat_summary(fun.y = mean, geom="point",colour="darkred", size=1, 
            position = position_dodge(width = .75)) +
          theme_apa() +
          geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
          coord_cartesian(ylim=c(-100, 100)) +
          scale_y_continuous(breaks = c( 0, seq(-90, 90, 20))) +
          # guide_legend(keywidth = .5, keyheight = .5) +       
          theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.9),
                legend.position = c(0.02,.98), 
                legend.key.height = unit(x = .17, units = "in")) +
          ylab("Percent Relative Bias") +
          xlab("Factor Loadings") +
          scale_fill_discrete(name="Estimator",
                              labels=c("FIML", "Goldstein-MIIV", "MUML-MIIV"))
  return(p)
}


```

```{r, echo = FALSE}
# finally saving the names of within and between loadings
wl <-c("L1 by Y1",
       "L1 by Y2",
       "L1 by Y3",
       "L1 by Y5",
       "L2 by Y4",
       "L2 by Y5",
       "L2 by Y6",
       "L2 by Y2")
bl <- c("LB by Y1",
       "LB by Y2",
       "LB by Y3",
       "LB by Y4",
       "LB by Y5",
       "LB by Y6")
```

# true model
Here I am going to ignore the effects of skew, unbalance, and just look at relative bias and rmse for truemodels across sample sizes


```{r plots, echo = FALSE, fig.height=10, fig.width=10}
l_sub <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults/trueModelComparisons.rds")
```

## Figure 1
```{r, echo = FALSE, fig.height=6, fig.width=12}
# save default par
def_par <- par()
par(pin = c(6, 12))

makeRelBiasPlot(l_sub, "cluster")
ggsave("RelBias_trueModel.png")

sargPlotTrue <- makeSargPlot(l_sub, facetVar = "cluster")
ggsave(filename = "Sargan_trueModel.png", plot = sargPlotTrue)


```


```{r summarystats, echo = FALSE}
# now computing summary stats by group
r <- l_sub %>%
  group_by(cluster, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            mean = mean(est, na.rm = TRUE),
            se = sd(est, na.rm = TRUE),
            meanBias = mean(p_relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))

# collecting just the loadings
rp <- r[r$parameter %in% c(bl, wl), ]

# reshaping wide by estimator
# ------------------------------------------------------------------------------
bias <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "meanBias" )
# bias <- as.matrix(bias, )
colnames(bias) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# ------------------------------------------------------------------------------
rmse <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "rmse" )
# rmse <- as.matrix(rmse)
colnames(rmse) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))

# -----------------------------------------------------------------------------
# Check Standard Errors
# take the se from r
rSe <- r[r$parameter %in% paste0(c(bl, wl)," se"), ]
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "mean")]
rSe$parameter <- substr(rSe$parameter, 0, 8)
rSe$meanSE <- rSe$mean
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "meanSE")]

se <- merge(rp, rSe)
se$EmpSe_mnSe <- paste0(formatC(round(se$se, 2),     format='f', digits=2), 
                        " (", 
                        formatC(round(se$meanSE, 3), format='f', digits=2), 
                        ")")



se <- reshape2::dcast(se, parameter ~ cluster + estimators, 
                        value.var = "EmpSe_mnSe" )
colnames(se) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
```

## Table 1: True Model Relative Bias

```{r, echo = FALSE}
knitr::kable(bias, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 2: True Model RMSE

```{r, echo = FALSE}
knitr::kable(rmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  # column_spec(2:4, bold = T, color = "white", background = "#D7261E") %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 3: True Model Standard Errors table (Emp_sd (meanSE))

```{r, echo = FALSE}
knitr::kable(se, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```


# MisSpecW1
## relative bias plots

note that the non-finite values warning here is for the missing loading L1 by y5 (7200 are those, then 5 that are apparently problematic)


```{r MisSpecW1 plots, echo = FALSE, fig.height=10, fig.width=10}
l_sub <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults/misW1Comparisons.rds")
```

## Figure 2 : Misspecification #1
```{r, echo = FALSE, fig.height=6, fig.width=12}
# save default par
def_par <- par()
par(pin = c(6, 12))

makeRelBiasPlot(l_sub, "cluster")
ggsave("RelBias_misspec1.png")

sargPlotMis1 <- makeSargPlot(l_sub, facetVar = "cluster")
ggsave(filename = "Sargan_Mis1.png", plot = sargPlotMis1)


```


```{r MisSpecW1 summarystats, echo = FALSE}
# now computing summary stats by group
r <- l_sub %>%
  group_by(cluster, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            mean = mean(est, na.rm = TRUE),
            se = sd(est, na.rm = TRUE),
            meanBias = mean(p_relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))

# collecting just the loadings
rp <- r[r$parameter %in% c(bl, wl), ]

# reshaping wide by estimator
# ------------------------------------------------------------------------------
bias <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "meanBias" )
# bias <- as.matrix(bias, )
colnames(bias) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# ------------------------------------------------------------------------------
rmse <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "rmse" )
# rmse <- as.matrix(rmse)
colnames(rmse) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# -----------------------------------------------------------------------------
# Check Standard Errors
# take the se from r
rSe <- r[r$parameter %in% paste0(c(bl, wl)," se"), ]
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "mean")]
rSe$parameter <- substr(rSe$parameter, 0, 8)
rSe$meanSE <- rSe$mean
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "meanSE")]

se <- merge(rp, rSe)
se$EmpSe_mnSe <- paste0(formatC(round(se$se, 2),     format='f', digits=2), 
                        " (", 
                        formatC(round(se$meanSE, 3), format='f', digits=2), 
                        ")")

se <- reshape2::dcast(se, parameter ~ cluster + estimators, 
                        value.var = "EmpSe_mnSe" )
colnames(se) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
```

## Table 4: Bias table

```{r, echo = FALSE}
knitr::kable(bias, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 5: RMSE

```{r, echo = FALSE}
knitr::kable(rmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 6: Standard Errors (Emp_sd (meanSE))

```{r, echo = FALSE}
knitr::kable(se, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

# MisSpecW2

## relative bias plots

note that the non-finite values warning here is for the missing loading L1 by y5 (7200 are those, then 5 that are apparently problematic)

```{r MisSpecW2 plots, echo = FALSE, fig.height=10, fig.width=10}
l_sub <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults/misW2Comparisons.rds")
```

## Figure 3 : Misspecification #2
```{r, echo = FALSE, fig.height=6, fig.width=12}
# save default par
def_par <- par()
par(pin = c(6, 12))

makeRelBiasPlot(l_sub, "cluster")
ggsave("RelBias_misspec2.png")

sargPlotMis2 <- makeSargPlot(l_sub, facetVar = "cluster")
ggsave("sargan_mis2.png", plot = sargPlotMis2)

```


```{r MisSpecW2 summarystats, echo = FALSE}
# now computing summary stats by group
r <- l_sub %>%
  group_by(cluster, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            mean = mean(est, na.rm = TRUE),
            se = sd(est, na.rm = TRUE),
            meanBias = mean(p_relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))

# collecting just the loadings
rp <- r[r$parameter %in% c(bl, wl), ]

# reshaping wide by estimator
# ------------------------------------------------------------------------------
bias <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "meanBias" )
# bias <- as.matrix(bias, )
colnames(bias) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# ------------------------------------------------------------------------------
rmse <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "rmse" )
# rmse <- as.matrix(rmse)
colnames(rmse) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# -----------------------------------------------------------------------------
# Check Standard Errors
# take the se from r
rSe <- r[r$parameter %in% paste0(c(bl, wl)," se"), ]
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "mean")]
rSe$parameter <- substr(rSe$parameter, 0, 8)
rSe$meanSE <- rSe$mean
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "meanSE")]

se <- merge(rp, rSe)
se$EmpSe_mnSe <- paste0(formatC(round(se$se, 2),     format='f', digits=2), 
                        " (", 
                        formatC(round(se$meanSE, 3), format='f', digits=2), 
                        ")")

se <- reshape2::dcast(se, parameter ~ cluster + estimators, 
                        value.var = "EmpSe_mnSe" )
colnames(se) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
```

## Table 7: bias

```{r, echo = FALSE}
knitr::kable(bias, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 8: RMSE table

```{r, echo = FALSE}
knitr::kable(rmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 9: SE table (Emp_sd (meanSE))

```{r, echo = FALSE}
knitr::kable(se, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```


# MisSpecW3

## relative bias plots

note that the non-finite values warning here is for the missing loading L1 by y5 (7200 are those, then 5 that are apparently problematic)

```{r MisSpecW3 plots, echo = FALSE, fig.height=10, fig.width=10}
l_sub <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults/misW3Comparisons.rds")
```

## Figure 4 : Misspecification #3
```{r, echo = FALSE, fig.height=6, fig.width=12}
# save default par
def_par <- par()
par(pin = c(6, 12))

makeRelBiasPlot(l_sub, "cluster")
ggsave("RelBias_misspec3.png")

sargPlotMis3 <- makeSargPlot(l_sub, facetVar = "cluster")
ggsave("sargan_mis3.png", plot = sargPlotMis3)

```


```{r MisSpecW3 summarystats, echo = FALSE}
# now computing summary stats by group
r <- l_sub %>%
  group_by(cluster, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            mean = mean(est, na.rm = TRUE),
            se = sd(est, na.rm = TRUE),
            meanBias = mean(p_relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))

# collecting just the loadings
rp <- r[r$parameter %in% c(bl, wl), ]

# reshaping wide by estimator
# ------------------------------------------------------------------------------
bias <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "meanBias" )
# bias <- as.matrix(bias, )
colnames(bias) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# ------------------------------------------------------------------------------
rmse <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "rmse" )
# rmse <- as.matrix(rmse)
colnames(rmse) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# -----------------------------------------------------------------------------
# Check Standard Errors
# take the se from r
rSe <- r[r$parameter %in% paste0(c(bl, wl)," se"), ]
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "mean")]
rSe$parameter <- substr(rSe$parameter, 0, 8)
rSe$meanSE <- rSe$mean
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "meanSE")]

se <- merge(rp, rSe)
se$EmpSe_mnSe <- paste0(formatC(round(se$se, 2),     format='f', digits=2), 
                        " (", 
                        formatC(round(se$meanSE, 3), format='f', digits=2), 
                        ")")

se <- reshape2::dcast(se, parameter ~ cluster + estimators, 
                        value.var = "EmpSe_mnSe" )
colnames(se) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
```

## Table 10 bias 

```{r, echo = FALSE}
knitr::kable(bias, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 11 RMSE

```{r, echo = FALSE}
knitr::kable(rmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 12 Standard Errors (Emp_sd (meanSE))

```{r, echo = FALSE}
knitr::kable(se, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```


# Skew/Kurtosis

There wasn't too much effect here honestly. In future studies it might be worth pushing around a bit more. But for the time being at least we know that these are at least mildly robust to skew/kurtosis.

Results here are for cells with 100 clusters of 30. I thought that was the most interesting. CN = 100; CS = 100 was too large, CN = 30; CS = 30 was too small (still looked ok though).

## relative bias plots

```{r skew kurt plots, echo = FALSE, fig.height=10, fig.width=10}
l_sub <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults/skewKurt.rds")
```

## Figure 5 : Skew/Kurtosis

```{r, echo = FALSE, fig.height=6, fig.width=12}
# save default par
def_par <- par()
par(pin = c(6, 12))

makeRelBiasPlot(l_sub, "skewKurt2")
ggsave("RelBias_skewkurt.png")

# p1 <- ggplot(l_sub[l_sub$parameter %in% wl, ], aes(x=parameter, y = p_relBias, fill = estimators)) +
#           geom_boxplot() +
#           # facet_grid(.~clusterSize + clusterN) +
#           facet_grid(.~skewKurt, scales="free_x", space="free_x", shrink=TRUE, drop=TRUE) +  
#           stat_summary(fun.y = mean, geom="point",colour="darkred", size=1, 
#             position = position_dodge(width = .75)) +
#           geom_hline(yintercept = 20) + 
#           geom_hline(yintercept = -20) + 
#           geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
#           coord_cartesian(ylim=c(-100, 100)) +
#           scale_y_continuous(breaks = seq(from = -100, to = 100, by = 20)) +
#           theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5),
#                 legend.position = 'none') +
#           ylab("Percent Relative Bias") +
#           xlab("Within Loadings")
# #ggsave(filename = "c:/users/Michael/desktop/plot.jpg")
# 
# p2 <- ggplot(l_sub[l_sub$parameter %in% bl,], aes(x=parameter, y = p_relBias, fill = estimators)) +
#         geom_boxplot() +
#         facet_grid(.~skewKurt) + 
#         stat_summary(fun.y = mean, geom="point",colour="darkred", size=1, 
#           position = position_dodge(width = .75)) +
#         geom_hline(yintercept = 20) + 
#         geom_hline(yintercept = -20) + 
#         geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
#         coord_cartesian(ylim=c(-100, 100)) +
#         scale_y_continuous(breaks = seq(from = -100, to = 100, by = 20)) +
#         theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
#         ylab(NULL) +
#         xlab("Between Loadings")
# 
# gridExtra::grid.arrange(p1, p2, ncol = 2)
#ggsave(filename = "c:/users/Michael/desktop/plot.jpg", plot = p3, width = 14, height = 6)

sargPlotSkew <- makeSargPlot(l_sub, facetVar = "skewKurt2")
ggsave(filename = "Sargan_skewKurtosis.png", plot = sargPlotSkew)


```


```{r skewkurt summarystats, echo = FALSE}
# now computing summary stats by group
r <- l_sub %>%
  group_by(cluster, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            mean = mean(est, na.rm = TRUE),
            se = sd(est, na.rm = TRUE),
            meanBias = mean(p_relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))

# collecting just the loadings
rp <- r[r$parameter %in% c(bl, wl), ]

# reshaping wide by estimator
# ------------------------------------------------------------------------------
bias <- reshape2::dcast(rp, parameter ~ skewKurt + estimators, 
                        value.var = "meanBias" )
# bias <- as.matrix(bias, )
colnames(bias) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# ------------------------------------------------------------------------------
rmse <- reshape2::dcast(rp, parameter ~ skewKurt + estimators, 
                        value.var = "rmse" )
# rmse <- as.matrix(rmse)
colnames(rmse) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# ------------------------------------------------------------------------------
# -----------------------------------------------------------------------------
# Check Standard Errors
# take the se from r
rSe <- r[r$parameter %in% paste0(c(bl, wl)," se"), ]
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "mean")]
rSe$parameter <- substr(rSe$parameter, 0, 8)
rSe$meanSE <- rSe$mean
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "meanSE")]

se <- merge(rp, rSe)
se$EmpSe_mnSe <- paste0(formatC(round(se$se, 2),     format='f', digits=2), 
                        " (", 
                        formatC(round(se$meanSE, 3), format='f', digits=2), 
                        ")")

se <- reshape2::dcast(se, parameter ~ skewKurt + estimators, 
                        value.var = "EmpSe_mnSe" )
colnames(se) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))

```

## Table 13: bias 

```{r, echo = FALSE}
knitr::kable(bias, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_header_above(c(" " = 1, 
                     "0000 - MVN" = 3, 
                     "0028 - btw skew" = 3, 
                     "2800 - within skew" = 3,
                     "2828 both skew" = 3))
```

## Table 14: RMSE 

```{r, echo = FALSE}
knitr::kable(rmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_header_above(c(" " = 1, 
                     "0000 - MVN" = 3, 
                     "0028 - btw skew" = 3, 
                     "2800 - within skew" = 3,
                     "2828 both skew" = 3))
```

## Table 15: SE  (Emp_sd (meanSE))

```{r, echo = FALSE}
knitr::kable(se, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_header_above(c(" " = 1, 
                     "0000 - MVN" = 3, 
                     "0028 - btw skew" = 3, 
                     "2800 - within skew" = 3,
                     "2828 both skew" = 3))
```

# Balance/Unbalance


## relative bias plots

```{r balance plots, echo = FALSE, fig.height=10, fig.width=10}
l_sub <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults/unbalance.rds")
```


## Figure 6 : Unbalance

```{r, echo = FALSE, fig.height=6, fig.width=12, warning=FALSE}
# save default par
def_par <- par()
par(pin = c(6, 12))

makeRelBiasPlot(l_sub, "cluster")
ggsave("RelBias_unbalance.png")

sargPlotBal <- makeSargPlot(l_sub, facetVar = "cluster")
ggsave(filename = "Sargan_Bal.png", plot = sargPlotBal)
```


```{r balance summarystats, echo = FALSE}
# now computing summary stats by group
r <- l_sub %>%
  group_by(cluster, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            mean = mean(est, na.rm = TRUE),
            se = sd(est, na.rm = TRUE),
            meanBias = mean(p_relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))

# collecting just the loadings
rp <- r[r$parameter %in% c(bl, wl), ]

# reshaping wide by estimator
# ------------------------------------------------------------------------------
bias <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "meanBias" )
# bias <- as.matrix(bias, )
colnames(bias) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# ------------------------------------------------------------------------------
rmse <- reshape2::dcast(rp, parameter ~ cluster + estimators, 
                        value.var = "rmse" )
# rmse <- as.matrix(rmse)
colnames(rmse) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
# -----------------------------------------------------------------------------
# Check Standard Errors
# take the se from r
rSe <- r[r$parameter %in% paste0(c(bl, wl)," se"), ]
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "mean")]
rSe$parameter <- substr(rSe$parameter, 0, 8)
rSe$meanSE <- rSe$mean
rSe <- rSe[, c("cluster", "clusterBal", "skewKurt", "modelSpec", "estimators",
  "parameter", "meanSE")]

se <- merge(rp, rSe)
se$EmpSe_mnSe <- paste0(formatC(round(se$se, 2),     format='f', digits=2), 
                        " (", 
                        formatC(round(se$meanSE, 3), format='f', digits=2), 
                        ")")

se <- reshape2::dcast(se, parameter ~ cluster + estimators, 
                        value.var = "EmpSe_mnSe" )
colnames(se) <- c("parameter", rep(c("FIML", "Gold", "MUML"), 4))
```

## Table 16: bias 

```{r, echo = FALSE}
knitr::kable(bias, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 17: RMSE table

```{r, echo = FALSE}
knitr::kable(rmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

## Table 18: Standard Errors (Emp_sd (meanSE))

```{r, echo = FALSE}
knitr::kable(se, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(2:4, bold = T, color = "red") %>%
  add_header_above(c(" " = 1, 
                     "CN = 100; CS = 100" = 3, 
                     "CN = 100; CS = 30" = 3, 
                     "CN = 30; CS = 100" = 3,
                     "CN = 30; CS = 30" = 3))
```

# Figure 7: Sargan's test True Model

```{r, fig.height=6, fig.width=12, echo = FALSE}
sargPlotTrue
# sargPlotMis1
# sargPlotMis2
# sargPlotMis3
```

# Figure 8: Sargan's Misspecified #1

```{r, fig.height=6, fig.width=12, echo = FALSE}
# sargPlotTrue
sargPlotMis1
# sargPlotMis2
# sargPlotMis3
```

# Figure 9: Sargan's test Misspecified #2

```{r, fig.height=6, fig.width=12, echo = FALSE}
# sargPlotTrue
# sargPlotMis1
sargPlotMis2
# sargPlotMis3
```

# Figure 10: Sargan's test Misspecified #3

```{r, fig.height=6, fig.width=12, echo = FALSE}
# sargPlotTrue
# sargPlotMis1
# sargPlotMis2
sargPlotMis3
```

# Figure: Sargan's test for skew/kurtosis

```{r, fig.height=6, fig.width=12, echo = FALSE}
# sargPlotTrue
# sargPlotMis1
# sargPlotMis2
sargPlotSkew
```

# Figure: Sargan's test for Unbalanced

```{r, fig.height=6, fig.width=12, echo = FALSE}
# sargPlotTrue
# sargPlotMis1
# sargPlotMis2
sargPlotBal
```



