---
title: "Masters results"
author: "Michael Giordano"
date: "April 3, 2018"
output: html_document
---

```{r setup, include=FALSE}
# setup
rm(list=ls())
library(tidyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(MIIVsem)
library(knitr)
library(kableExtra)
options(knitr.table.format = "html") 
baseDir <- "c:/users/mgiordan/git/mlmcfasimulation/fullSim"
setwd(baseDir)
```

ToDo:
summarize non-convergence
Work in emp Se's vs mean se's


```{r, include=FALSE}
# ------------------------------------------------------------------------
# set up df to everything else
# read in all results
dm <- readRDS("c:/users/mgiordan/git/mlmcfasimulation/fullSim/finalResults/allResultsDf.rds")
# convert all to character
dm[, ] <- lapply(dm[, ], as.character)
# make all long
allLong <- gather(dm, parameter, est, l1.by.y1:lb.by.y6.sarg.p, factor_key = FALSE)
# only convert estimate to numeric
allLong$est <- as.numeric(allLong$est)
# -----------------------------------------------------------------------
```

## Between cell conditions

```{r, echo = FALSE}
# names(dm)
kable(unique(dm[,c("clusterSize", "clusterN", "clusterBal", "skewKurt")]), row.names = FALSE)
```

## Within Cell Conditions

```{r, echo = FALSE}
# names(dm)
kable(unique(dm[,c("modelSpec", "estimators")]), row.names = FALSE)
```

# subsetting just the factor loadings and cleaning those

```{r, echo = FALSE}
# saving the names of all loadings (to subset just these parameters)
l <- c("l1.by.y1",
       "l1.by.y2",
       "l1.by.y3",
       "l1.by.y5",
       "l2.by.y4",
       "l2.by.y5",
       "l2.by.y6",
       "l2.by.y2",
       "l1.by.y3",
       "lb.by.y1",
       "lb.by.y2",
       "lb.by.y3",
       "lb.by.y4",
       "lb.by.y5",
       "lb.by.y6")
loadings <- allLong[allLong$parameter %in% l, ]
# put in the true values
loadings[loadings$parameter=="l1.by.y1", "true"] <- 1
loadings[loadings$parameter=="l1.by.y2", "true"] <- .8
loadings[loadings$parameter=="l1.by.y3", "true"] <- .7
loadings[loadings$parameter=="l2.by.y4", "true"] <- 1
loadings[loadings$parameter=="l2.by.y5", "true"] <- .8
loadings[loadings$parameter=="l2.by.y6", "true"] <- .7
loadings[loadings$parameter=="l1.by.y5", "true"] <- .3
loadings[loadings$parameter=="l2.by.y2", "true"] <- .3
# tru values for between parameters
loadings[loadings$parameter=="lb.by.y2", "true"] <- .7
loadings[loadings$parameter=="lb.by.y3", "true"] <- .6
loadings[loadings$parameter=="lb.by.y4", "true"] <- .8
loadings[loadings$parameter=="lb.by.y5", "true"] <- .7
loadings[loadings$parameter=="lb.by.y6", "true"] <- .8
# Remove the scaling indicators
loadings <- loadings[which(loadings$parameter!="l1.by.y1"),]
loadings <- loadings[which(loadings$parameter!="l2.by.y4"),]
loadings <- loadings[which(loadings$parameter!="lb.by.y1"),]
#relative bias
loadings$relBias <- (loadings$est - loadings$true) / loadings$true

# finally saving the names of within and between loadings
wl <-c("l1.by.y1",
       "l1.by.y2",
       "l1.by.y3",
       "l1.by.y5",
       "l2.by.y4",
       "l2.by.y5",
       "l2.by.y6",
       "l2.by.y2")
bl <- c("lb.by.y1",
       "lb.by.y2",
       "lb.by.y3",
       "lb.by.y4",
       "lb.by.y5",
       "lb.by.y6")

loadings$cluster <- as.factor(paste0(loadings$clusterN,"groups_of_N", loadings$clusterSize))
# getting the order right
loadings$cluster <- relevel(loadings$cluster, " 30groups_of_N 30")
loadings$cluster <- relevel(loadings$cluster, " 30groups_of_N100")
loadings$cluster <- relevel(loadings$cluster, "100groups_of_N 30")
loadings$cluster <- relevel(loadings$cluster, "100groups_of_N100")

```

# Step 1: true model
Here I am going to ignore the effects of skew, unbalance, and just look at relative bias and rmse for truemodels across sample sizes

```{r, echo = FALSE, fig.height=10, fig.width=10}
# Now we want to look at the best case
# no skew kurtosis
l_sub <- subset(loadings, loadings$skewKurt=="0000")
# only balanced clusters
l_sub <- subset(l_sub, l_sub$clusterBal=="bal")
# true model
l_sub <- subset(l_sub, l_sub$modelSpec=="trueModel")

# first make relative bias plots (this is more intuitive than the tables)
ggplot(l_sub[l_sub$parameter %in% wl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  # facet_grid(.~clusterSize + clusterN) +
  facet_grid(.~cluster) +  
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-.5,.5), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Within: trueModel across sample sizes")
ggplot(l_sub[l_sub$parameter %in% bl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(.~cluster) + 
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-1,1), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Between: true model across sample sizes")


# now computing summary stats by group
r <- l_sub %>%
  group_by(clusterSize, clusterN, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            meanBias = mean(relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))
# reshaping wide by estimator
bias <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "meanBias" )
names(bias)[4:6] <- paste0(names(bias)[4:6], "bias")
rmse <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "rmse" )
names(rmse)[4:6] <- paste0(names(rmse)[4:6], "rmse")
# merging these together
biasandrmse <- merge(bias, rmse, by = c("clusterSize", "clusterN", "parameter"))
# sort
biasandrmse <- biasandrmse[order(biasandrmse$clusterSize, decreasing = TRUE), ]
biasandrmse <- biasandrmse[order(biasandrmse$clusterN, decreasing = TRUE), ]
# re number rows?
# making a nice table
knitr::kable(biasandrmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1:2, bold = T, border_right = F) %>%
  column_spec(3,   bold = T, border_right = F) %>%
  column_spec(4:6, width = "30em", background = "yellow") %>%
  group_rows("Cell 1", 1, 11) %>%
  group_rows("Cell 2", 12, 22) %>%
  group_rows("Cell 3", 23, 33) %>%
  group_rows("Cell 4", 34, 44)
  
```


# MisSpecW1

```{r, echo = FALSE}
# Now we want to look at the best case
# no skew kurtosis
l_sub <- subset(loadings, loadings$skewKurt=="0000")
# only balanced clusters
l_sub <- subset(l_sub, l_sub$clusterBal=="bal")
# true model
l_sub <- subset(l_sub, l_sub$modelSpec=="misSpecW1")

# first make relative bias plots (this is more intuitive than the tables)
ggplot(l_sub[l_sub$parameter %in% wl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterSize~clusterN) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-.5,.5), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Within: misSpecW1 across sample sizes")
ggplot(l_sub[l_sub$parameter %in% bl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterSize~clusterN) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-1,1), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Between: misSpecW1 model across sample sizes")


# now computing summary stats by group
r <- l_sub %>%
  group_by(clusterSize, clusterN, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            meanBias = mean(relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))
# reshaping wide by estimator
bias <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "meanBias" )
names(bias)[4:6] <- paste0(names(bias)[4:6], "bias")
rmse <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "rmse" )
names(rmse)[4:6] <- paste0(names(rmse)[4:6], "rmse")
# merging these together
biasandrmse <- merge(bias, rmse, by = c("clusterSize", "clusterN", "parameter"))
# sort
biasandrmse <- biasandrmse[order(biasandrmse$clusterSize, decreasing = TRUE), ]
biasandrmse <- biasandrmse[order(biasandrmse$clusterN, decreasing = TRUE), ]
# re number rows?
# making a nice table
knitr::kable(biasandrmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1:2, bold = T, border_right = F) %>%
  column_spec(3,   bold = T, border_right = F) %>%
  column_spec(4:6, width = "30em", background = "yellow") %>%
  group_rows("Cell 1", 1, 11) %>%
  group_rows("Cell 2", 12, 22) %>%
  group_rows("Cell 3", 23, 33) %>%
  group_rows("Cell 4", 34, 44)
  
```


# MisSpecW2

```{r, echo = FALSE}
# Now we want to look at the best case
# no skew kurtosis
l_sub <- subset(loadings, loadings$skewKurt=="0000")
# only balanced clusters
l_sub <- subset(l_sub, l_sub$clusterBal=="bal")
# true model
l_sub <- subset(l_sub, l_sub$modelSpec=="misSpecW2")

# first make relative bias plots (this is more intuitive than the tables)
ggplot(l_sub[l_sub$parameter %in% wl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterSize~clusterN) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-.5,.5), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Within: misSpecW2 across sample sizes")
ggplot(l_sub[l_sub$parameter %in% bl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterSize~clusterN) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-1,1), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Between: misSpecW2 model across sample sizes")


# now computing summary stats by group
r <- l_sub %>%
  group_by(clusterSize, clusterN, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            meanBias = mean(relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))
# reshaping wide by estimator
bias <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "meanBias" )
names(bias)[4:6] <- paste0(names(bias)[4:6], "bias")
rmse <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "rmse" )
names(rmse)[4:6] <- paste0(names(rmse)[4:6], "rmse")
# merging these together
biasandrmse <- merge(bias, rmse, by = c("clusterSize", "clusterN", "parameter"))
# sort
biasandrmse <- biasandrmse[order(biasandrmse$clusterSize, decreasing = TRUE), ]
biasandrmse <- biasandrmse[order(biasandrmse$clusterN, decreasing = TRUE), ]
# re number rows?
# making a nice table
knitr::kable(biasandrmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1:2, bold = T, border_right = F) %>%
  column_spec(3,   bold = T, border_right = F) %>%
  column_spec(4:6, width = "30em", background = "yellow") %>%
  group_rows("Cell 1", 1, 11) %>%
  group_rows("Cell 2", 12, 22) %>%
  group_rows("Cell 3", 23, 33) %>%
  group_rows("Cell 4", 34, 44)
  
```

# MisSpecW3

```{r, echo = FALSE}
# Now we want to look at the best case
# no skew kurtosis
l_sub <- subset(loadings, loadings$skewKurt=="0000")
# only balanced clusters
l_sub <- subset(l_sub, l_sub$clusterBal=="bal")
# true model
l_sub <- subset(l_sub, l_sub$modelSpec=="misSpecW3")

# first make relative bias plots (this is more intuitive than the tables)
ggplot(l_sub[l_sub$parameter %in% wl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterSize~clusterN) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-.5,.5), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Within: misSpecW3 across sample sizes")
ggplot(l_sub[l_sub$parameter %in% bl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterSize~clusterN) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-1,1), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Between: misSpecW3 model across sample sizes")


# now computing summary stats by group
r <- l_sub %>%
  group_by(clusterSize, clusterN, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            meanBias = mean(relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))
# reshaping wide by estimator
bias <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "meanBias" )
names(bias)[4:6] <- paste0(names(bias)[4:6], "bias")
rmse <- reshape2::dcast(r, clusterSize + clusterN + parameter ~ estimators, value.var = "rmse" )
names(rmse)[4:6] <- paste0(names(rmse)[4:6], "rmse")
# merging these together
biasandrmse <- merge(bias, rmse, by = c("clusterSize", "clusterN", "parameter"))
# sort
biasandrmse <- biasandrmse[order(biasandrmse$clusterSize, decreasing = TRUE), ]
biasandrmse <- biasandrmse[order(biasandrmse$clusterN, decreasing = TRUE), ]
# re number rows?
# making a nice table
knitr::kable(biasandrmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1:2, bold = T, border_right = F) %>%
  column_spec(3,   bold = T, border_right = F) %>%
  column_spec(4:6, width = "30em", background = "yellow") %>%
  group_rows("Cell 1", 1, 11) %>%
  group_rows("Cell 2", 12, 22) %>%
  group_rows("Cell 3", 23, 33) %>%
  group_rows("Cell 4", 34, 44)
  
```

# Skew/Kurtosis

There wasn't too much effect here honestly. In future studies it might be worth pushing around a bit more. But for the time being at least we know that these are at least mildly robust to skew/kurtosis.

Results here are for cells with 100 clusters of 30. I thought that was the most interesting. 100 of 100 was too large, 30 of 30 was too small (still looked ok though).

```{r, echo = FALSE}
# Now we want to look at the best case
# no skew kurtosis
# l_sub <- subset(loadings, loadings$skewKurt=="0000")
# only balanced clusters
l_sub <- subset(loadings, loadings$clusterBal=="bal")
# true model
l_sub <- subset(l_sub, l_sub$modelSpec=="trueModel")
# maybe just subset the largest N
l_sub <- subset(l_sub, l_sub$clusterSize==" 30")
l_sub <- subset(l_sub, l_sub$clusterN=="100")

l_sub$cluster <- paste0(l_sub$clusterN, "of", l_sub$clusterSize)

# first make relative bias plots (this is more intuitive than the tables)
ggplot(l_sub[l_sub$parameter %in% wl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterBal~skewKurt) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-.5,.5), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Within: Skew Kurtosis")
ggplot(l_sub[l_sub$parameter %in% bl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterBal~skewKurt) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-1,1), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Between: Skew Kurtosis")


# now computing summary stats by group
r <- l_sub %>%
  group_by(clusterSize, clusterN, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            meanBias = mean(relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))
# reshaping wide by estimator
bias <- reshape2::dcast(r, clusterSize + clusterN + parameter + skewKurt ~ estimators, value.var = "meanBias" )
names(bias)[4:6] <- paste0(names(bias)[4:6], "bias")
rmse <- reshape2::dcast(r, clusterSize + clusterN + parameter + skewKurt ~ estimators, value.var = "rmse" )
names(rmse)[4:6] <- paste0(names(rmse)[4:6], "rmse")
# merging these together
biasandrmse <- merge(bias, rmse, by = c("clusterSize", "clusterN", "parameter"))
# sort
biasandrmse <- biasandrmse[order(biasandrmse$clusterSize, decreasing = TRUE), ]
biasandrmse <- biasandrmse[order(biasandrmse$clusterN, decreasing = TRUE), ]
# re number rows?
# making a nice table
knitr::kable(biasandrmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1:2, bold = T, border_right = F) %>%
  column_spec(3,   bold = T, border_right = F) %>%
  column_spec(4:6, width = "30em", background = "yellow") %>%
  group_rows("Cell 1", 1, 11) %>%
  group_rows("Cell 2", 12, 22) %>%
  group_rows("Cell 3", 23, 33) %>%
  group_rows("Cell 4", 34, 44)
  
```


# Balance/Unbalance


```{r, echo = FALSE}
# Now we want to look at the best case
# no skew kurtosis
l_sub <- subset(loadings, loadings$skewKurt=="0000")
# only balanced clusters
# l_sub <- subset(loadings, loadings$clusterBal=="bal")
# true model
l_sub <- subset(l_sub, l_sub$modelSpec=="trueModel")
# maybe just subset the largest N
# l_sub <- subset(l_sub, l_sub$clusterSize==" 30")
# l_sub <- subset(l_sub, l_sub$clusterN=="100")

l_sub$cluster <- paste0(l_sub$clusterN, "of", l_sub$clusterSize)

# first make relative bias plots (this is more intuitive than the tables)
ggplot(l_sub[l_sub$parameter %in% wl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterBal~skewKurt) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-.5,.5), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Within: Balanced vs Unbalanced")
ggplot(l_sub[l_sub$parameter %in% bl,], aes(x=parameter, y = relBias, fill = estimators)) +
  geom_boxplot() +
  facet_grid(clusterBal~skewKurt) +
  geom_hline(yintercept = .2) + 
  geom_hline(yintercept = -.2) + 
  geom_hline(yintercept = 0, color = "red", linetype = "dashed") +
  scale_y_continuous(limits = c(-1,1), breaks = seq(from = -.8, to = .8, by = .2)) +
  theme(axis.text.x=element_text(angle=45,hjust=1,vjust=0.5)) +
  ggtitle("Between: Balanced vs Unbalanced")


# now computing summary stats by group
r <- l_sub %>%
  group_by(clusterSize, clusterN, clusterBal, skewKurt, modelSpec, estimators, parameter) %>%
  summarize(count = n(),
            meanBias = mean(relBias, na.rm = TRUE), 
            rmse = sqrt(sum((est-true)^2, na.rm = TRUE)/n()))
# reshaping wide by estimator
bias <- reshape2::dcast(r, clusterSize + clusterN + parameter + skewKurt ~ estimators, value.var = "meanBias" )
names(bias)[4:6] <- paste0(names(bias)[4:6], "bias")
rmse <- reshape2::dcast(r, clusterSize + clusterN + parameter + skewKurt ~ estimators, value.var = "rmse" )
names(rmse)[4:6] <- paste0(names(rmse)[4:6], "rmse")
# merging these together
biasandrmse <- merge(bias, rmse, by = c("clusterSize", "clusterN", "parameter"))
# sort
biasandrmse <- biasandrmse[order(biasandrmse$clusterSize, decreasing = TRUE), ]
biasandrmse <- biasandrmse[order(biasandrmse$clusterN, decreasing = TRUE), ]
# re number rows?
# making a nice table
knitr::kable(biasandrmse, digits = 3, row.names = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  column_spec(1:2, bold = T, border_right = F) %>%
  column_spec(3,   bold = T, border_right = F) %>%
  column_spec(4:6, width = "30em", background = "yellow") %>%
  group_rows("Cell 1", 1, 11) %>%
  group_rows("Cell 2", 12, 22) %>%
  group_rows("Cell 3", 23, 33) %>%
  group_rows("Cell 4", 34, 44)
  
```

